\documentclass[notopicbreak,contbibnum,plain]{simplecv}
\usepackage{times}
\usepackage{fullpage}
\usepackage[resetlabels]{multibib}
%\usepackage{multibib}
\renewcommand{\topicmargin}{0.10\columnwidth}
%\renewcommand{\topicmargin}{0.001\columnwidth}
%\newlength{\t@picmargin}


\newcites{refpaper}{vitae}
\newcites{unrefpaper}{vitae}
\newcites{journal}{Journal}
\newcites{techreport}{vitae}
\newcites{submitpaper}{vitae}
\newcites{classproject}{vitae}
\newcites{conference}{vitae}


\begin{document}
\leftheader{7 Caroline St\\ 
Newport, NP20 1EQ\\
United Kingdom\\[.35ex]
Tel~: +44 7931842955\\
Web~: \small http://ril.newport.ac.uk/sarker} 
%Fax~: +44 1633 432307}

\rightheader{Cognitive Robotics Research Centre\\
University of Wales, Newport,\\
Newport Business School, Allt-yr-yn Campus\\
Newport, NP20 5DA, United Kingdom\\
Email~: \small Mdomarfaruque.Sarker@newport.ac.uk}%\\

%
%\title{\Large \textsc{Md Omar Faruque Sarker}}
\title{\Large Md Omar Faruque Sarker}
%
\maketitle
%Some people put a summary here. Note: there are many \LaTeX{}
%variables you can set in the preamble to change the look of the CV.
\vspace*{-1cm}
%=================================================
\section{\textsc{Education}}
\label{edu}
\begin{topic}
    \item \emph{Ph.D. Robotics (Multi-robot system)}, 
    University of Wales, Newport, UK\\
    Thesis: \textit{Self-regulated Multi-robot 				Task~Allocation}, 2010
%        \item  Supervisor: Dr Torbjørn S. Dahl
%        \item  Co-supervisors: Dr Christopher A.J. Tubb and Dr Ann Smith
\vspace*{-0.1cm}
%-------------------------------------------------    
    \item \emph{M.Eng. HCI \& Robotics},  
    Korea Institute of Science \& Technology,\\ University of Science \& Technology, South Korea, 2007\\ 
        Thesis: \textit{A Knowledge-Based Service Approach
for Human-Centered Robots}\\
%        \item Supervisor: Dr. ChangHwan Kim
Graduate courses: \emph{Human Machine Interaction, Intelligent Control, Mobile Robotics,\\ Computer Vision, Advanced Symbolic AI
Techniques} and \emph{Information Security}. CGPA: 4.18/4.5
\vspace*{-0.1cm}
%-------------------------------------------
    \item \emph{B.Sc. Mechanical Engineering},
    Bangladesh University of Engineering and Technology, 2005\\       
Final-year elective courses: \emph{Mechatronics} and \emph{Bio-Engineering}
%CGPA: 3.11/4.0
\end{topic}
%%========================
\section{\textsc{Employment}}
\vspace*{-0.1cm}
\begin{topic}
	\item[10/2007 - present] \textit{PhD Student/ Research Assistant (Full-time)}\\
    Cognitive Robotics Research Centre,
    University of Wales, Newport, UK (\small http://ril.newport.ac.uk)
 	%http://ril.newport.ac.uk/\\
    %Responsibilities: Setup a large multi-robot system and develop software framework to validate an 	interdisciplinary model of division of labour under the collaborative EPSRC project ``Defying the Rules -How Self -Organizing Systems Work'' (EP/E061982/1).
    \vspace*{-0.1cm}
    \normalsize    
    \item[05/2010 - 08/2010] \textit{Summer-of-code Student (Part-time),}
    Google Inc.  USA (\small http://socghop.appspot.com)
\vspace*{-0.1cm}
 \normalsize 
	    \item[05/2009 - 08/2009] \textit{Summer-of-code Student  (Part-time),}
    Google Inc.  USA (\small http://socghop.appspot.com)
\vspace*{-0.1cm}
 \normalsize      
    \item[08/2005 - 07/2007] \textit{Postgraduate Research Assistant/ Visiting Research Scientist (Full-time)\\}
    Center for Cognitive Robotics Research,
    Korea Institute of Sci. \& Tech., S. Korea (\small humanoid.kist.re.kr)
\vspace*{-0.1cm}
 \normalsize 
\item[03/2005 - 07/2005] \textit{Lecturer and Coordinator, Industrial Training Program (Part-time)}\\
	Dept. of CSE, Int'l Islamic University of Chittagong, Dhaka campus, Bangladesh (\small www.iiucdc.org)
\vspace*{-0.1cm}
 \normalsize     
    \item[10/2004 - 05/2005] \textit{Project Engineer (Full-time) }\\
	Institute of Info \& Comm. Tech.,
	Bangladesh Univ. of Engg. \& Tech. (\small www.buet.ac.bd/iict)
\vspace*{-0.1cm}
 \normalsize 
	\item[05/2004 - 09/2004]\textit{ Systems Engineer (Part-Time)}
	Ektoo Ltd., Dhaka, Bangladesh (\small www.ektoo.net.bd)
\vspace*{-0.1cm}
 \normalsize 
	\item[11/2002 - 04/2004] \textit{Associate Editor (Part-Time)}
	Technology Today Ltd., Bangladesh (\small www.techtodaybd.com)
\vspace*{-0.1cm}
 \normalsize 
	\item[04/2002--06/2004] \textit{Tutor (Part-time)}
	 Institute of Info \& Comm. Tech.,
	Bangladesh Univ. of Engg. \& Tech.
\vspace*{-0.2cm}
 \normalsize 
	\item[10/2002--04/2004] \textit{System Administrator (Part-time)}
	 EasySoft Networks Ltd. Dhaka, Bangladesh.
\end{topic}
%\vspace*{-0.1cm}
%===================================================
\section{\textsc{Awards}}
\vspace*{-0.1cm}
\label{awards}
\begin{topic}
\item[10/2010 - Present] 
    \emph{University of Wales, Newport, UK Research Support Grant}
\vspace*{-0.1cm}
\item[10/2007 - 09/2010] 
    \emph{EPSRC, UK PhD Studentship  (Grant ref. EP/E061982/1)}
    %http://gow.epsrc.ac.uk/ViewGrant.aspx?GrantRef=EP/E061982/1
\vspace*{-0.1cm}
\item[05/2010 - 08/2010] 
    \emph{Google Summer of Code Open-source Software Development Sponsorship for Tahoe-LAFS}	%http://socghop.appspot.com/gsoc/student\_project/show/google/gsoc2010/tahoe\_lafs/t127230764024
\vspace*{-0.1cm}
\item[05/2009 - 08/2009] 
    \emph{Google Summer of Code Open-source Software Development Sponsorship for Bluez}
%    http://socghop.appspot.com/gsoc/student\_project/show/google/gsoc2009/bluez/t124021929557    
\vspace*{-0.1cm}
\item[09/2005 - 08/2007] 
    \emph{Korea Institute of Science \& Technology - Int'l R \& D Academy Postgraduate Scholarship}
    %http://irda.kist.re.kr	     
\vspace*{-0.1cm}
\item[07/2000 - 06/2004] 
    \emph{Bangladesh University of Engineering \& Technology Technical Scholarship}
\vspace*{-0.1cm}    
\item[1997] 
\emph{District Commissioner's Gold Medal Honour for the Best Student of the Year} 	
\vspace*{-0.1cm}
\item[1996] 
	\emph{Prime Minister's Award for  Merit List Position in SSC Examination}
\vspace*{-0.1cm}
\item[1995] 
	\emph{International Friendship Award, Scouts
Invitation Program, Boy Scouts of Nippon, Japan}
\end{topic}  
%========================================================
\renewcommand{\topicmargin}{0.0\columnwidth}
%\section{Interests}
%\begin{topic}
\section{\textsc{Research Interests}}
\begin{topic}
\normalsize
\vspace*{-0.3cm}
\item \textbf{Cloud Computing:} \textit{Distributed \& parallel processing, optimization and security for clouds and large grids.}\\
\textbf{AI:} \textit{Knowledge representation, reasoning, searching techniques, semantic web \& intelligent grid technologies.}\\
\textbf{Robotics:} \textit{Bio-inspired self-organized pattern formation, matching and task-allocation in multi-agent systems.}
%\\
%
%\textbf{Networking:} \textit{Scalable distributed processing for complex networks and clouds.}\\
%\textbf{Computer vision and image processing:}\textit{ Multi-agent tracking and real-time image processing.}
%\end{topic}
%\vspace*{0.1cm}
%\item \textbf{\textsc{Teaching Interests}}\\ Computer Networks, Information Security, Network Programming, Artificial Intelligence, Mobile Robotics,\\ Intelligent Control, Applied Computer Vision and Multi-agent Systems.
\vspace*{-0.25cm}
\end{topic}
%===================================================
\section{\textsc{Technical Skills/Tools}}
\vspace*{-0.3cm}
\begin{topic}
\item \textbf{Programming/Scripting Languages:}\\
- Proficient: \textit{Python, C/C++,  Prolog, Unix Shell scripts, HTML, PHP, XML, SQL, UML, LaTeX.}\\
- Familiar: \textit{Java, RDF, SAPQL, CSS, AJAX, MATLAB, Tcl/Tk}
\vspace*{-0.2cm}
\item  \textbf{Open Source Tools/Frameworks}:\\ 
- \textit{Twisted, Nevow, Django} Python web frameworks\\ 
- \textit{SciPy, NumPy, Matplotlib} Python  scientific libraries\\
- Python \textit{mock} testing abd d-bus interprocess communication libraries\\ 
- \textit{Git, Darcs, SVN} revision control systems\\ 
- \textit{Drupal, razorCMS, SkyBlueCanvas} content management systems\\ 
- \textit{Boost, wxWidget} C++ libraries\\ 
- \textit{Prot\'{e}g\'{e}-OWL} ontology editor, \textit{CLIPS, FuzzyCLIPS} inference engines, \textit{CORAL and XSB}  deductive databases\\%/logic programming systems\\
- Popular Unix/Linux networking/database servers: e.g. \textit{Apache, BIND, MySQL, SQUID, NFS, SAMBA etc.\\
- Linux Netfilter/IPTables} security package\\ 
- \textit{OpenCV} computer vision library, \textit{SwisTrack}  multi-robot tracker\\ 
- \textit{Epuck, Myro and Player/Stage} robot control frameworks\\ 
- \textit{NetLogo} multi-agent simulator\\ 
- \textit{Xenomai} Linux based real-time OS, \textit{Bluez} Bluetooth stack, and TCP/IP sockets\\
- \textit{SQLite/PostgreSQL RDBMS}\\ 
- \textit{Tahoe-LAFS} distributed peer-to-peer file system\\ 
- \textit{Dia and Umbrello} UML authoring tools.
%
\vspace*{-0.3cm}
\end{topic}
\vspace*{-0.3cm}

%\section{References}
%\begin{topic}
%\item Available upon request (please e-mail me).
%\end{topic}
%================================================
\section{\textsc{Completed software development projects}}
\vspace*{-0.2cm}
\section{\textbf{\underline{PhD Research Projects} (http://github.com/roboshepherd)}}
\begin{topic}
\vspace*{-0.3cm}
\item \textbf{[1] Project title: \textit{E-puck Robot's Centralized and Distributed Controller Development}}\\
Achievements: Developed the task achieving behaviours of the e-puck robot (navigation, obstacle avoidance and homing) and integrated with SwisTrack tracker\\
Tools/Skills: Python, C/C++, DBus, Git (version control system).
\vspace*{-0.2cm}
\item \textbf{[2] Project title: \textit{SwisTrack Multi-robot Tracker's Prosilica GigE Camera Driver and DBus Wrapper Development}}\\
Achievements: Developed GigE camera driver using Prosilica's Linux-SDK and OpenCV. Implemented SwisTrack's DBus server component for broadcasting position information to robot controllers\\
Tools/Skills: C++, Python, Git, OpenCV (computer vision library).
\vspace*{-0.3cm}
\end{topic}
\section{\textbf{\underline{Google Summer-of-Code Projects}} (http://socghop.appspot.com)}
\vspace*{-0.3cm}
%%----------------------
\textbf{[1] 2010 Project title: \textit{A Publish/Subscribe Style Decentralized Introduction}}\\
Organization: Tahoe-LAFS (http://tahoe-lafs.org/trac/tahoe-lafs/ticket/68)\\
Achievements: Designed, developed, tested and documented the community demanded fault-tolerant multiple-introducer scheme (ticket \#68)\\
Tools/Skills: Python, Twisted/Nevow (web framework), Mock (code testing), Darcs (version control system).\\
%%
\textbf{[2] 2009 Project title: \textit{A One-Step Bluetooth Device Setup Wizard Using 2D Data-matrix symbol}}\\
Organization: BlueZ (http://www.bluez.org)\\
Achievements: Tested the feasibility developing a user-friendly one-step setup wizard and integrating short-range wireless NFC technology with Bluez's Linux-Bluetooth-stack\\
Tools/Skills: C, Bluetooth specification version 2.1 EDR, 2D DataMatrix library (libdmtx), Git.
\vspace*{-0.3cm}
%% Masters course
\section{\textbf{\underline{Masters Course Projects}}}
\vspace*{-0.3cm}
\textbf{[1] Project title: \textit{Application Development for Intelligent LEGO Home}}\\
Achievements: Developed an inference engine, a Java client to Prot\'{e}g\'{e} and several UPnP devices\\
Tools/Skills: Java, Prot\'{e}g\'{e}/OWL ontology editor, CLIPS inference engine, and Intel UPnP authoring tools.\\
\textbf{[2] Project title: \textit{Image Feature Extraction and Mobile Robot Path Planning}}\\
Achievements: Applied weighted and non-weighted least-square techniques, Hough transform for efficient line extraction. Implemented the gradient method for mobile robot path planning with wave-front propagation algorithm\\
Tools/Skills: MATLAB, Least square techniques, Hough transform, Gradient method.\\
\textbf{[3] Project title: \textit{Human Face Recognition}}\\
Achievements: Developed an algorithm for converting colour info from RGB to HSV colour space that made the face detection more robust in varying illuminations\\
Tools/Skills: C/C++, Tcl/Tk, Statistical histogram algorithm.\\
%\vspace*{-0.2cm}
\textbf{[4] Project title: \textit{Fourier 2D Transform tool}}\\
Achievements: Developed a tool that can transform a 64x64 image\\
Tools/Skills: C, Tcl/Tk, Fourier transform algorithm.
\vspace*{-0.3cm}
%\end{topic}
%% Masters research
\section{\textbf{\underline{Masters Research Projects}} (http://humanoid.kist.re.kr/new/eng/)}
\vspace*{-0.3cm}
\textbf{[1] Project title: \textit{Application Development for Human-Centered Service Robots}}\\
Achievements: Designed and developed Knowledge-based services and implemented two scenarios in an office and a hospital environment in Player/Stage mobile robot simulator\\
Tools/Skills: C++/Java, Prolog, and XML, Java-Player client library, XSB deductive database, XML-RPC, Evolution Robotics SDK, Wxwidget Library, Boost C++ Multi-thread library.\\
\textbf{[2] Project title: \textit{Intelligent Network Security System for Robots}}\\
Achievements: A knowledge-based security architecture was implemented and simulated\\
Tools/Skills: Unix BASH shell, SQL, CORAL, CLIPS, C, Linux Netfilter IPTables, CORAL deductive database, Fuzzy inference system, MySQL.\\
\textbf{[3] Project title:\textit{ Real-Time Robot Control}}\\
Achievements: Customized real-time IEEE 1394 device-driver in Linux for humanoid robot control\\
Tools/Skills: C, Linux/Xenomai RTOS, UML, Source-code-navigator.
\vspace*{-0.3cm}
%%
%===================================================
\section{\textsc{Publications}}
\vspace*{-0.3cm}
\begin{topic}
\item \textbf{Book Chapters}
	\vspace*{-0.2cm}
	\nocitejournal{Sarker2010ants}
    \nocitejournal{Sarker2006lncs}	
	\bibliographystylejournal{unsrt}
	\bibliographyjournal{vitae}
	\bibliography{vitae}
%\end{topic}
%
%\begin{topic}
\vspace*{-0.2cm}
\item \textbf{Conference Papers}
	\vspace*{-0.2cm}
    \nociterefpaper{Sarker2010control_vitae}
        \nociterefpaper{Sarker2009}
    \nociterefpaper{Sarker2007roman}
    \nociterefpaper{Sarker2006iros}
    \nociterefpaper{Sarker2006icm}
	\bibliographystylerefpaper{unsrt}
	\bibliographyrefpaper{vitae}
	\bibliography{vitae}
\vspace*{-0.2cm}		
\item \textbf{Technical Report and Thesis}
	\vspace*{-0.2cm}
    \nocitetechreport{sarker2008report}
    \nocitetechreport{sarker2007thesis}
    \bibliographystyletechreport{unsrt}
     \bibliographytechreport{vitae}
	\bibliography{vitae}
\vspace*{-0.2cm}
\item \textbf{Submitted/Accepted for Publication}
	\vspace*{-0.2cm}
    \nocitesubmitpaper{dahl2011}
    \nocitesubmitpaper{sarker2011}
    \bibliographystylesubmitpaper{unsrt}
    \bibliographysubmitpaper{vitae}
	\bibliography{vitae}
\end{topic}
%============================================

\end{document}
